---
title: "RPG_Modelling"
format: html
editor: visual
---

```{r}
#| echo: false
#| warning: false
#| message: false


# Prepare environment

# Clean memory 
rm(list=ls())
gc()

# Load package
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, broom, nnet, data.table, glue, gtsummary, here, sf, tmap, units, dplyr, modelsummary, fixest)

# List directories 
dir <- list()
dir$root <- here()
dir$data <- here(dir$root, "data")
dir$raw <- here(dir$data, "raw")
dir$derived <- here(dir$data, "derived")
dir$final <- here(dir$data, "final")
dir$script <- here(dir$root, "script")
dir$output <- here(dir$root, "output")

# Create non existing directories
lapply(dir, function(i) dir.create(i, recursive = T, showWarnings = F))
```

## Multinomial logit

In the literature, we can find land-share models using multinomial logit, where the producer chooses between different crops while maximising its expected profit. The outcome variable is the land allocated to the production of a given crop over the total cultivated area.

In our analysis, the dependent variable is `etat`, a categorical variable going from 1 to 4, which measures if the acreage destined to a crop in a commune has increased, decreased, been maintained or has never existed during our period of interest. We will try to explain this variable first with data on historical potential yields from the **GAEZ dataset**, as well as potential yield change, computed as the difference between the future potential yield under the RCP 8.5 climate change scenario of the HadGEM2-ES model and the historical values of potentiel yield.

```{r}
#| echo: false
#| warning: false
#| message: false

# Load dataset
df_final <- readRDS(here(dir$final, "Joined_GAEZ_RPG.rds"))

```

### Descriptive Statistics

```{r}
#| echo: false
#| warning: false
#| message: false

# % of communes in each category of our dependent variable by crop

table_etat <- df_final |>
  group_by(LIBELLE_GROUPE_CULTURE_AGG, etat_libelle) |>
  summarise(nb_communes = n_distinct(insee), .groups = "drop")

table_etat <- table_etat |>
  group_by(LIBELLE_GROUPE_CULTURE_AGG) |>
  mutate(
    total_communes = sum(nb_communes),
    pourcentage = round(100 * nb_communes / total_communes, 1)
  ) %>%
  ungroup()

table_pourcentages <- table_etat |>
  select(LIBELLE_GROUPE_CULTURE_AGG, etat_libelle, pourcentage) |>
  pivot_wider(names_from = etat_libelle, values_from = pourcentage, values_fill = 0) |>
  arrange(LIBELLE_GROUPE_CULTURE_AGG)

print(table_pourcentages)
```

### Potential yield change

```{r}
#| echo: false
#| warning: false
#| message: false

# making sure the dependent variable is a factor
df_final$etat_libelle <- as.factor(df_final$etat_libelle)

# set the baseline category 
df_final$etat_libelle <- relevel(df_final$etat_libelle, ref = "maintenu") 

logit_1 <- multinom(etat_libelle ~ value_hist_rpg + change, data = df_final)

```

**Notes : Coefficients issued from the `summary()` command cannot be interpreted directly, only significance level and sign of the coefficients are relevant. Relative risk ratio can be interpreted as the risk of switching to another category (if RRR \> 1, it is more likely that the crop in question in the given community will switch categories).**

### Comparative advantage difference

```{r}
#| echo: false
#| warning: false
#| message: false

# Adding the variable to the multinomial logit regression

logit_2 <- multinom(etat_libelle ~ AC_hist + AC_diff, data = df_final)
```

Crops with higher historical AC are less likely to appear or disappear compared to be maintained. In contrast, a higher future AC increases the likelihood of crop appearance and reduces the chance of disappearance, highlighting the anticipatory adaptation of communes to future agronomic potential. The change in crop share over time (change) also plays a role, with significant negative effects on both appearance and the “never cultivated” category, indicating that crops with strong shifts in area are more likely to be maintained. Although the coefficients on future potential yield (value_futur_rpg) are small, they are highly significant, and consistently associated with reduced odds of all categories compared to being maintained.

### Combining CAI and Potential yield change

```{r}
#| echo: false
#| warning: false
#| message: false

logit_3 <- multinom(etat_libelle ~ AC_hist + change, data = df_final)
```

When combining historical comparative advantage index with potentiel yield change as explanatory variables in the same model, we find similar results to **model 2**, where we wanted to explain acreage dynamics with historical comparative advantage index and its potential change. Crops with higher historical CA are more likely to be maintained than to appear or disappear, but are more likely to be never cultivated compared to being maintained. When potential yield change is higher, crop acreage is also less likely to vary compared to be maintained as it is.

### Adding climate controls

```{r}
#| echo: false
#| warning: false
#| message: false

# mean temperature control over the whole period 

logit_c1 <- multinom(etat_libelle ~ value_hist_rpg + change + moyenne_temp_period + moyenne_temp_ref + moyenne_precip_period + moyenne_precip_ref, data = df_final)

logit_c2 <- multinom(etat_libelle ~ AC_hist + AC_diff + moyenne_temp_period + moyenne_temp_ref + moyenne_precip_period + moyenne_precip_ref, data = df_final)

logit_c3 <- multinom(etat_libelle ~ AC_hist + change + moyenne_temp_period + moyenne_temp_ref + moyenne_precip_period + moyenne_precip_ref, data = df_final)

# Putting all models in a summary table

logit_models <- list(
  "1a" = logit_1,
  "2a" = logit_2,
  "3a" = logit_3,
  "1b" = logit_c1,
  "2b" = logit_c2,
  "3b" = logit_c3
)


modelsummary(logit_models,
             shape = term + response ~ model,
             stars = TRUE,
             statistic = "({std.error})",
             coef_map = c(
               "value_hist_rpg" = "Historical yield",
               "change" = "Potential yield change",
               "AC_hist" = "Historical CA",
               "AC_diff" = "Potential CA change",
               "moyenne_temp_period" = "Temperature mean",
               "moyenne_temp_ref" = "Reference temperature mean",
               "moyenne_precip_period" = "Mean precipitation",
               "moyenne_precip_ref" = "Reference mean precipitation"
  ),
  gof_omit = "AIC|BIC|Log.Lik",
  output = "markdown"
)

```

## Reproducing Cui et al.

Cui et al. uses a panel model where the author tries to explain acreage change of **corn** and **soybean** with variations in climate normals since the 1950s.

```{r}
#| echo: false
#| warning: false
#| message: false

# Load dataset
df_panel <- readRDS(here(dir$final, "Joined_GAEZ_RPG_Panel.rds"))

```

### Testing model fit

The first model looks at how climate variables affect crop acreage change. Specifically, we will be looking at **Wheat** and **Maize**, as they are the most cultivated crops in France, as well as showing a tendency of decreasing in agricultural surface occupied over our period of interest. Additionnal to Cui's model, we introduce potential yield change as an explanatory variable to see if there is anticipation effect from crop producers.

```{r}
#| echo: false
#| warning: false
#| message: false

df_panel_wheat <- df_panel |>
  filter(LIBELLE_GROUPE_CULTURE_AGG == "Blé tendre") |>
  group_by(insee) |>
  filter(any(surf_code_group_m2 > 0, na.rm = TRUE)) |> ## keep only communes that cultivated wheat at least once during the whole period
  ungroup()

## Baseline model

baseline_model_w <- feols(log_surf_agri ~ mean + value_hist_rpg_t_ha + reference_mean + total_precip_wet_days + reference_avg_total_precip_wet_days | year, data = df_panel_wheat, weights = ~surf_agri_geo_unit_m2)

## Adding interaction between temperature mean and potential yield change

interact_model_w1 <- feols(log_surf_agri ~ mean*change + value_hist_rpg_t_ha + mean*reference_mean + total_precip_wet_days + reference_avg_total_precip_wet_days | year, data = df_panel_wheat, weights = ~surf_agri_geo_unit_m2)

## Adding interaction between temperature mean and reference mean, as well as squared temperature for non-linear effect

interact_model_w2 <- feols(log_surf_agri ~ mean*change + I(mean^2) + value_hist_rpg_t_ha + mean*reference_mean + total_precip_wet_days + reference_avg_total_precip_wet_days | year, data = df_panel_wheat, weights = ~surf_agri_geo_unit_m2)

## Adding lagged temperature to see the effect of the previous year on acreage

df_panel_wheat <- df_panel_wheat |>
  arrange(insee, year) |>
  group_by(insee) |>
  mutate(temp_lag_1 = lag(mean, n = 1)) |>
  ungroup()

lag_model_w <- feols(log_surf_agri ~ l(mean, 0:1) + change + value_hist_rpg_t_ha + reference_mean + l(total_precip_wet_days, 0:1) + reference_avg_total_precip_wet_days | year, data = df_panel_wheat, panel.id = ~insee+year, weights = ~surf_agri_geo_unit_m2)

## All variables

complete_model_w <- feols(log_surf_agri ~ l(mean, 0:1) + I(mean^2) + mean*change + value_hist_rpg_t_ha + mean*reference_mean + l(total_precip_wet_days, 0:1) + reference_avg_total_precip_wet_days | year, data = df_panel_wheat, panel.id = ~insee+year, weights = ~surf_agri_geo_unit_m2)

models_cui_w <- list(
  "Wheat (Baseline)" = baseline_model_w,
  "Wheat (Interaction)" = interact_model_w1,
  "Wheat (Interactions + Squared)" = interact_model_w2,
  "Wheat (Lagged)" = lag_model_w,
  "Wheat (all var)" = complete_model_w
)

modelsummary(models_cui_w,
             stars = TRUE,
             statistic = "({std.error})",
             coef_map = c(
               "value_hist_rpg_t_ha" = "Historical yield (in t/ha)",
               "mean" = "Temperature mean",
               "reference_mean" = "Reference temperature mean",
               "total_precip_wet_days" = "Total precipitation",
               "reference_avg_total_precip_wet_days" = "Reference total precipitation",
               "change" = "Potential yield change",
               "mean:change" = "Interaction yield change x temperature",
               "mean:reference_mean" = "Interaction temperature x reference temp",
               "I(mean^2)" = "Squared mean temperature",
               "l(mean, 1)" = "Lagged temperature mean",
               "l(total_precip_wet_days, 1)" = "Lagged total precipitation"
  ),
  gof_omit = "AIC|BIC|Log.Lik",
  output = "markdown"
)

```

Historical yield consistently shows a positive and statistically significant effect on wheat acreage expansion across all models, indicating that communes with historically high yields tend to allocate more surface area to wheat. In contrast, the effect of potential yield change is consistently negative but not statistically significant on its own. However, its interaction with current mean annual temperature is both positive and significant, suggesting that in warmer communes, increases in potential yield have a stronger positive effect on wheat surface expansion.

Temperature variables display more nuanced effects. While current mean temperature has an inconsistent impact, historical temperature levels are systematically positive and highly significant, implying that warmer historical climates are associated with greater wheat cultivation. The interaction between current temperature and potential yield change reinforces this positive relationship. When a squared temperature term is introduced, the linear effect becomes non-significant, pointing to a potential non-linear relationship. Moreover, the interaction with reference (historical) temperature yields a significant negative coefficient, suggesting that in already warm communes, further temperature increases may reduce wheat acreage. A lagged effect of current temperature also appears: higher temperatures in the previous year correlate with reduced wheat acreage, significant at the 10% level.

Precipitation levels show a generally positive but mixed influence. Contemporary precipitation tends to be positively associated with wheat surface expansion, especially when lagged values are considered, which are both positive and strongly significant. In contrast, historical precipitation levels exhibit a significant negative relationship with wheat acreage, suggesting that areas with historically high rainfall may be less suited or less used for wheat cultivation.

### Crop-specific analysis

```{r}
#| echo: false
#| warning: false
#| message: false

# Executing regressions on our chosen variables : Maize and Oilseeds

df_panel_maize <- df_panel |>
  filter(LIBELLE_GROUPE_CULTURE_AGG == "Maïs grain et ensilage") |>
  group_by(insee) |>
  filter(any(surf_code_group_m2 > 0, na.rm = TRUE)) |>
  ungroup()

final_model_m <- feols(log_surf_agri ~ mean*change + I(mean^2) + value_hist_rpg_t_ha + mean*reference_mean + total_precip_wet_days + reference_avg_total_precip_wet_days | year, data = df_panel_maize, weights = ~surf_agri_geo_unit_m2)

df_panel_oilseed <- df_panel |>
  filter(LIBELLE_GROUPE_CULTURE_AGG == "Autres oléagineux") |>
  group_by(insee) |>
  filter(any(surf_code_group_m2 > 0, na.rm = TRUE)) |>
  ungroup()

final_model_o <- feols(log_surf_agri ~ mean*change + I(mean^2) + value_hist_rpg_t_ha + mean*reference_mean + total_precip_wet_days + reference_avg_total_precip_wet_days | year, data = df_panel_oilseed, weights = ~surf_agri_geo_unit_m2)

models_cui <- list(
  "Wheat" = interact_model_w2,
  "Maize" = final_model_m,
  "Oilseeds" = final_model_o
)

modelsummary(models_cui,
             stars = TRUE,
             statistic = "({std.error})",
             coef_map = c(
               "value_hist_rpg_t_ha" = "Historical yield (in t/ha)",
               "mean" = "Temperature mean",
               "reference_mean" = "Reference temperature mean",
               "total_precip_wet_days" = "Total precipitation",
               "reference_avg_total_precip_wet_days" = "Reference total precipitation",
               "change" = "Potential yield change",
               "mean:change" = "Interaction yield change x temperature",
               "mean:reference_mean" = "Interaction temperature x reference temp",
               "I(mean^2)" = "Squared mean temperature"
  ),
  gof_omit = "AIC|BIC|Log.Lik",
  output = "markdown"
)

```

Across all three models, historical yield (measured in tons per hectare) shows a consistently positive and statistically significant association with crop acreage, suggesting that communes with higher past yields tend to allocate more land to these crops. The coefficient on potential yield change differs substantially across crops: it is strongly positive for maize, negative for wheat and oilseed, though only significant for maize and oilseed. This implies that an increase in expected future yield would incentivize maize expansion but discourage oilseed and wheat in some contexts.

The interaction between potential yield change and current mean temperature is significant across all models, but with varying signs: positive for wheat and oilseed, negative for maize. This means that the influence of potential yield change on land allocation is modified by temperature, and the effect differs by crop.

Temperature mean itself does not have a significant or consistent effect, and its sign varies by crop. In contrast, the historical temperature mean is strongly positive and significant for wheat and maize, implying that areas with historically warmer climates tend to devote more land to these crops—particularly wheat. The interaction between mean temperature and reference temperature is also significant for wheat and oilseed. For wheat, the strongly negative coefficient suggests that current warmth may reduce acreage especially in areas that were already warm in the past. The squared mean temperature term is significant and positive for wheat, and marginally so for oilseed, suggesting potential non-linear effects of temperature on land allocation decisions for these crops.

Total precipitation and its reference value show more variable patterns. While total precipitation has a marginally significant positive effect on oilseed acreage, the reference precipitation has a strong negative effect for wheat, possibly indicating that areas with historically wetter conditions allocate less land to wheat.

### Non-linearity analysis

To further analyse the non-linear effect of temperature on crop acreage of **Wheat**, **Maize** and **Oilseeds**, we implement a binned scatterplot regression to visualize the relationship between the variables, by grouping a variable that measures the number of days in a given temperature level into bins and plotting the average outcome in each bin.

```{r}
#| echo: false
#| warning: false
#| message: false


binned_regw <- feols(log_surf_agri ~ total_precip_wet_days + days_bin_lower_0 + days_bin_0_3 + days_bin_3_6 + days_bin_6_9 + days_bin_9_12 + days_bin_12_15 + days_bin_15_18 + days_bin_18_21 + days_bin_21_24 + days_bin_24_27 + days_bin_27_30 | year, data = df_panel_wheat, weights = ~surf_agri_geo_unit_m2)

# Get coefficients
coefs <- tidy(binned_regw, conf.int = TRUE)

# Keep only the bin terms
coefs_bins <- coefs |>
  filter(grepl("^days_bin", term)) |>
  mutate(
    bin = gsub("days_bin_", "", term),
    bin = factor(bin, levels = gsub("days_bin_", "", term))  # keep order
  )

# Plot
ggplot(coefs_bins, aes(x = bin, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "firebrick") +
  labs(
    x = "Temperature bin (over 3-day periods)",
    y = "Effect on log(crop acreage)",
    title = "Estimated Effect of Temperature Bins on Wheat Acreage"
  ) +
  theme_minimal()

```
